Data Prep

### 2024-01-17 00.0_dataPrep.qmd
committed to this order for now

I suppose we could leave in the low fix rate individuals, especially for co-roosting. \[Actually, maybe we should leave them in for co-roosting, but not the others... which makes me think maybe we should leave them in for roost and social, just not movement, because they can contribute to the background information. Aaaarrrrrrggghhhhh.... XXX\]

@@

```{r}
# Get elevation rasters ---------------------------------------------------
sf <- map(removed_too_few_days, ~st_as_sf(.x, coords = c("location_lat", "location_long"), remove = F, crs = "WGS84"))
elevs_z10 <- map(sf, ~elevatr::get_elev_raster(.x , z = 10))
save(elevs_z10, file = "data/dataPrep/elevs_z10.Rda")
```

```{r}
load("data/dataPrep/elevs_z10.Rda")
```

@@

# tidy up
rm(removed_too_few_days)
rm(sf)
rm(elevs_z10)
rm(groundElev_z10)
rm(with_altitudes)
```

>>>>

@@

```{r}
#| eval: false
# Get elevation rasters ---------------------------------------------------
sf <- map(removed_too_few_days, ~st_as_sf(.x, coords = c("location_lat", "location_long"), remove = F, crs = "WGS84"))
elevs_z10 <- map(sf, ~elevatr::get_elev_raster(.x , z = 10))
save(elevs_z10, file = "data/dataPrep/elevs_z10.Rda")
save(sf, file = "data/dataPrep/sf.Rda")
```

```{r}
load("data/dataPrep/elevs_z10.Rda")
load("data/dataPrep/sf.Rda")
```

@@

# tidy up
rm(removed_too_few_days)
rm(sf)
rm(elevs_z10)
rm(groundElev_z10)
rm(with_altitudes)
gc()
```
